FoRTE Disturbance Paper Analysis

### 2021-10-29 C.analysis/paper_analysis.Rmd

```{r}
annual_met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(year, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total winnd", 
         variable = "grd") -> 
  wind_df

@@

monthly_met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(month, mon_time, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total winnd", 
         variable = "grd") -> 
  wind_df

@@

@@

  ggplot() + 
  geom_line(data = to_plot, aes(year, value, group = met), 
            alpha = 0.9, color = "#999999", ) + 
  geom_pointrange(data = obs, aes(x=year, y=mean, ymin=lower, ymax=upper)) + 
  facet_wrap("description", scales = "free", 
             labeller = label_glue('({.l}) {description}')) +
  THEME +
  labs(y = "", x = "Year")  + 
  theme(legend.position = "none") -> 
  plot

@@

resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.2) + 
  stat_cor(method = "pearson", 
           aes(label = ..r.label..),
           size = 3, 
           label.y.npc = "bottom",
           r.accuracy = 0.01) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
    facet_wrap("variable", 
               scales = "free", 
               labeller = label_glue('({.l}) {variable}')) + 
  guides(colour = guide_legend("Severity")) -> 
  plot
  ggsave(plot, filename = "figures/resistance_resilience3.png", width = 6, height = 4.5)

>>>>

```{r}
annual_met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(year, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total wind", 
         variable = "grd") -> 
  wind_df

@@

monthly_met %>% 
  filter(variable %in% c("ugrd", "vgrd")) %>% 
  mutate(value = value^2) %>% 
  group_by(month, mon_time, met) %>% 
  summarise(value = sqrt(sum(value))) %>% 
  ungroup() %>%
  mutate(units = "m s-1", 
         description = "total wind", 
         variable = "grd") -> 
  wind_df

@@

chrono <- rbind(
  data.frame(value = c(0.55, 1.35, 1.30, 0.80, 0.45, 1.53), 
             year = c(6, 24, 50, 56, 68, 85), 
           variable = "NEP", 
           description = "NEP\n (MgC ha-1 year-1)"), 
  data.frame(value = c(5.07, 5.13, 5.44, 5.27,  5.04, 6.54),
             year = c(6, 24, 50, 56, 68, 85), 
             variable = "NPP",        
             description = "NPP\n (MgC ha-1 year-1)"), 
    data.frame(value = c(4.52, 3.78, 4.14, 4.47, 4.59, 5.01),
             year = c(6, 24, 50, 56, 68, 85), 
             variable = "Rh",        
             description = "Rh\n (MgC ha-1 year-1)"))

chrono$year <- chrono$year + 1900

# read in other UMBS data 
read.csv(file.path(BASE_DIR, "C.analysis", "UMBS_data",
                   "US-UMB_AnnualNEP_2002-2019.csv")) %>%
  tidyr::gather(c("NEP", "RE", "GPP"), key = "variable", value = "value") %>%  
  filter(variable  %in% c("GPP", "NPP", "Rh", "NEP")) %>% 
  mutate(description = paste0(variable, '\n (MgC ha-1 year-1)')) -> 
  more_obs

@@

  ggplot() + 
  geom_line(data = to_plot, aes(year, value, group = met), 
            alpha = 0.9, color = "#999999") + 
  geom_pointrange(data = obs, aes(x=year, y=mean, ymin=lower, ymax=upper)) + 
  geom_line(data = more_obs, aes(Year, value), color = "black") + 
  geom_point(data = chrono, aes(year, value), color = "red") + 
  facet_wrap("description", scales = "free", 
             labeller = label_glue('({.l}) {description}')) +
  THEME +
  labs(y = "", x = "Year")  + 
  theme(legend.position = "none") -> 
  plot

@@

resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.2, show_guide  = FALSE) + 
  stat_cor(method = "pearson", 
           aes(label = ..r.label..),
           size = 3, 
           label.y.npc = "bottom",
           r.accuracy = 0.01, 
            show_guide  = FALSE) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
    facet_wrap("variable", 
               scales = "free", 
               labeller = label_glue('({.l}) {variable}')) + 
  guides(colour = guide_legend("Severity")) ->
  plot
  ggsave(plot, 
         filename = "figures/resistance_resilience3.png", width = 6, height = 4.5)
